Hybrid Threads for the Parrot Virtual Machine

### 2012-03-08 Paper.tex
Improved Design of GC section

In previous attempts to implement threading support in Parrot, the answer to this problem was to disable the garbage collector while multiple threads are active. Other VMs solve this problem by suspending all threads while the GC is running. While multithreaded garbage collection algorithms exist, their implementation would have been to complex and brittle for this paper\cite{VCGC}.

@@

Separation of memory domains is a problem for objects which are only referenced from other threads. But since all objects which could be accessed from other threads have to be pushed onto the Task object representing such threads, they can still be referenced from there.

>>>>

In previous attempts to implement threading support in Parrot, the answer to this problem was to disable the garbage collector while multiple threads are active. While multithreaded garbage collection algorithms exist, their implementation would have been too complex and brittle for this paper\cite{VCGC}. Other VMs solve this problem by suspending all threads while the GC is running. Suspending all threads is not as simple as it sounds because these threads can be in any state at the time. For example, they could be blocking on some long running I/O operation like waiting for a reply on a network connection. A thread can stay in this condition indefinitely thereby never being able to confirm synchronization.

@@

With separated memory domains it can happen that an object is created on one thread, used on another thread but not any more on the owner thread. Without any additional measures, the GC would collect such objects, since it does not know about references from other threads. But since all objects which could be accessed from other threads have to be pushed onto the Task object representing these threads, the objects can still be referenced from the Task object. Since the task is still owned by the original thread, the GC knows that these objects are still in use.
